---
title: "HW2"
author: "Kate Kong jk49633"
date: "2024-01-28"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

profs <- read.csv('profs.csv')
bikeshare <- read.csv('bikeshare.csv')
capmetro <- read.csv('capmetro_UT.csv')
billboard <- read.csv('billboard.csv')

library(ggplot2)
library(dplyr)

options(dplyr.summarise.inform = FALSE)
```

# Link to the GitHub
[GitHub](https://github.com/katekong27/SDS_315.git)


# **Question 1**

Part A. Create a histogram to display the overall data distribution of course evaluation scores.

```{r echo=FALSE}
plot <- ggplot(profs)
plot + geom_histogram(aes(x=eval, fill = 'lightcoral'), bins = 60) + labs(title = "Distribution of Course Evaluation Scores", x = "Score", y = "Frequency") + theme_classic()
```

The graph above represents the distribution of course evaluation scores for `r nrow(profs)` professors at the University of Texas at Austin.



Part B. Use side-by-side boxplots to show the distribution of course evaluation scores by whether or not the
professor is a native English speaker.

```{r echo=FALSE}
plot + geom_boxplot(aes(x = eval, y = native), fill = 'lightcoral') + labs(title = "Distribution of Course Evaluation Scores for Native and Non-Native English Speaking Professors", x = "Score", y = "Native English Speaker")
```

The side-by-side boxplots show the distribution of course evaluation scores for professors at the University of Texas at Austin, and they are divided by whether they are native English speakers or not. 



Part C. Use a faceted histogram with two rows to compare the distribution of course evaluation scores for
male and female instructors.

```{r echo=FALSE}
plot + geom_histogram(aes(x=eval, fill = 'lightcoral'), bins = 60) + labs(title = "Distribution of Course Evaluation Scores By Gender of the Professor", x = "Score", y = "Frequency") + facet_wrap(~gender)
```

The two graphs show the distribution of course evaluation scores of UT professors. The graph on the left shows the scores of female professors, while the graph on the right shows the scores of male professors. 



Part D. Create a scatterplot to visualize the extent to which there may be an association between the
professor’s physical attractiveness (x) and their course evaluations (y)

```{r echo=FALSE}
plot + geom_point(aes(x = beauty, y = eval), col = 'lightcoral') + labs(title = "Relationship Between the Attractiveness and Course Evaluation Scores of Professors", x = "Attractiveness", y = "Course Evaluation Score")
```

The scatterplot above shows the relationship between physical attractiveness of UT professors and their course evaluation scores. The correlation coefficient between the two variables is `r cor(profs$beauty, profs$eval)`, indicating the attractiveness of the professor has little impact on his or her course evaluation score. 

# **Question 2**

Plot A: a line graph showing average hourly bike rentals (total) across all hours of the day (hr).

```{r echo=FALSE}
mean_rentals = bikeshare %>%
  group_by(hr) %>%
  summarize(count = n(), hourly_rentals = mean(total, na.rm = TRUE))

ggplot(mean_rentals) + geom_line(aes(x = hr, y = hourly_rentals), col = 'navy') + labs(title = "Average Hourly Bike Rentals Across All Hours of the Day", x = "Hour of the Day", y = "Average Bike Rentals")
```

The line graph above illustrates the trend in the average bike rentals for every hour of the day. It can be seen that the number of rental rises steeply between 5 and 8 AM, decreases a little from 8 AM to 10 AM. A relatively steady number is maintanied from 10 AM to 3 PM. At 3 PM the average number of bike rentals rise more, and it plummets after 5 PM.



Plot B: a faceted line graph showing average bike rentals by hour of the day, faceted according to
whether it is a working day (workingday).

```{r echo=FALSE}
mean_rentals = bikeshare %>%
  group_by(hr, workingday) %>%
  summarize(count = n(),
            hourly_rentals = mean(total, na.rm = TRUE))

ggplot(mean_rentals) + geom_col(aes(x = hr, y = hourly_rentals), fill = 'navy') + labs(title = "Average Hourly Bike Rentals on Working Days and Weekends Across All Hours of the Day", x = "Hour of the Day", y = "Average Bike Rentals") + facet_wrap(~workingday)
```

The two graphs above show the average number of bike rentals per every hour of the day, divided into whether it is working day or not. The graph for working days has 1 written on top of it while the one for weekends/holidays has 0 assigned to it. The graph for the weekends have a relatively normal distribution of average bike rentals as indicated by the bell curve shown in the graph. On the other hand, the graph for the working days has a bimodal distribution since it has 2 peaks.


Plot C: a faceted bar plot showing average ridership (y) during the 9 AM hour by weather situation
code (weathersit, x), faceted according to whether it is a working day or not. (Remember that you
can focus on a specific subset of rows of a data set using filter.)

```{r echo=FALSE}
nine_am_rentals = bikeshare %>%
  filter(hr == 9) %>%
  group_by(weathersit, workingday) %>%
  summarize(count = n(),
            hourly_rentals = mean(total, na.rm = TRUE))

ggplot(nine_am_rentals) + geom_col(aes(x = weathersit, y = hourly_rentals), fill = 'navy') + labs(title = "Average Hourly Depending on Weather Situation on Working Days and Weekends", x = "Weather Situation", y = "Average Bike Rentals") + facet_wrap(~workingday)
```

The two graphs above the average number of bike rentals at 9 AM on working days and weekends depending on the weather situation. 0 on the at the top of the left graph indicates that it represents the data for weekends and holidays whereas the 1 on the right graph shows it is for the working days. Furthermore, 1 for the weather means clear weather, 2 means light mist and clouds, and 3 means light snow/rain. 

# **Question 3**

Your task in this problem is to make two faceted plots and to answer questions about them.

1. One faceted line graph that plots average boardings by hour of the day, day of week, and month. You
should facet by day of week. Each facet should include three lines of average boardings (y) by hour of
the day (x), one line for each month and distinguished by color. Give the figure an informative caption
in which you explain what is shown in the figure and also address the following questions, citing evidence
from the figure. Does the hour of peak boardings change from day to day, or is it broadly similar across
days? Why do you think average boardings on Mondays in September look lower, compared to other
days and months? Similarly, why do you think average boardings on Weds/Thurs/Fri in November
look lower? (Hint: wrangle first, then plot.)

```{r echo=FALSE, warning=FALSE}
average_boarding = capmetro %>%
  group_by(hour_of_day, month, day_of_week) %>%
  summarize(hourly_rentals = mean(boarding, na.rm = TRUE)) %>%
  arrange(day_of_week)

ggplot(average_boarding) + geom_line(aes(x = hour_of_day, y = hourly_rentals, color = month)) + scale_color_brewer(type='qual') + scale_y_log10() + labs(title = "Average Hourly CapMetro Boardings For Every Hour of the Day", x = "Hour of the Day", y = "Average Boardings") + facet_wrap(~day_of_week)
```
The graphs above show the trend for average CapMetro Boardings for each day of the week and the month. The hours of peak boarding looks similar among weekdays and between the two weekends, but there is a huge discrepency between weekdays and weekends. The average boardings on Mondays in September might be lower due to the temperature being high enough for people to want to stay indoors; there could also be other confounding variables. Furthermore, the average boardings on Tuesdays, Wednesdays, and Thurdays of November look lower because a lot of students go home and are not in Austin due to Thanksgiving Break. 



2. One faceted scatter plot showing boardings (y) vs. temperature (x), faceted by hour of the day, and
with points colored in according to whether it is a weekday or weekend. Give the figure an informative
caption in which you explain what is shown in the figure and also answer the following question, citing
evidence from the figure. When we hold hour of day and weekend status constant, does temperature
seem to have a noticeable effect on the number of UT students riding the bus?

```{r echo=FALSE}
boarding_temperature = capmetro %>%
  group_by(temperature, hour_of_day, weekend) %>%
  summarize(hourly_boarding = mean(boarding, na.rm = TRUE)) %>%
  arrange(hour_of_day)

ggplot(boarding_temperature) + geom_point(aes(x = temperature, y = hourly_boarding, color = weekend)) + scale_color_brewer(type='qual') + scale_y_log10() + labs(title = "Average Hourly CapMetro Boarding Based on Temperature", x = "Temperature", y = "Average Hourly CapMetro Boardings") + facet_wrap(~hour_of_day)
```
The graphs above show the average hourly CapMetro boardings by temperature for every hour of the day from 6 AM to 21 AM (9 PM). Overall, the correlation coefficient between the temperature and the average hourly boarding is `r cor(boarding_temperature$temperature, boarding_temperature$hourly_boarding)`, which is a relatively low number and illustrates that there is a weak relationship between the two variables. However, one clear trend that is consistent throughout the graphs is that no matter the time of the dat, weekdays have higher average CapMetro Boardings than do weekends. A possible cause behind this is that people tend to stay home and move less on the weekends than the weekdays. All in all, the temperature does not seem to have a noticeable effect on the number of UT students riding the bus. 



# **Question 4**

Part A: Make a table of the top 10 most popular songs since 1958, as measured by the total number of weeks
that a song spent on the Billboard Top 100. Note that these data end in week 22 of 2021, so the most popular
songs of 2021 onwards will not have up-to-the-minute data; please send our apologies to The Weeknd.
Your table should have 10 rows and 3 columns: performer, song, and count, where count represents the
number of weeks that song appeared in the Billboard Top 100. Make sure the entries are sorted in descending
order of the count variable, so that the more popular songs appear at the top of the table. Give your table a
short caption describing what is shown in the table.
(Note: you’ll want to use both performer and song in any group_by operations, to account for the fact that
multiple unique songs can share the same title.)

```{r echo=FALSE}
top_song = billboard %>%
  group_by(song, performer) %>%
  summarize(count_total = max(weeks_on_chart)) %>%
  arrange(desc(count_total))
top_song[1:10,]
```

The table above lists 10 songs that spent the longest amount of time (measured in weeks) on the Billboard Top 100 chart. The song titles are accompanied by the artist that sang the song and the number of weeks they spent on the chart.


Part B: Is the “musical diversity” of the Billboard Top 100 changing over time? Let’s find out. We’ll measure
the musical diversity of given year as the number of unique songs that appeared in the Billboard Top 100 that
year. Make a line graph that plots this measure of musical diversity over the years. The x axis should show
the year, while the y axis should show the number of unique songs appearing at any position on the Billboard
Top 100 chart in any week that year. For this part, please filter the data set so that it excludes the years
1958 and 2021, since we do not have complete data on either of those years. Give the figure an informative
caption in which you explain what is shown in the figure and comment on any interesting trends you see.

There are number of ways to accomplish the data wrangling here. We offer you two hints on two possibilities:

  1) You could use two distinct sets of data-wrangling steps. The first set of steps would get you a table
that counts the number of times that a given song appears on the Top 100 in a given year. The second
set of steps operate on the result of the first set of steps; it would count the number of unique songs
that appeared on the Top 100 in each year, irrespective of how many times it had appeared.

  2) You could use a single set of data-wrangling steps that combines the length and unique commands.
  
```{r echo=FALSE}
billboard_2 = billboard %>%
  filter(year != 1958 & year != 2021) %>%
  group_by(song, performer, year) %>%
  summarize(count_times = n())

music_diversity = billboard_2 %>%
  group_by(year) %>%
  summarize(total = n())

ggplot(music_diversity) + geom_line(aes(x = year, y = total), col = 'pink') + labs(title = "Distribution of Unique Songs that Appeared on Billboard Top 100 Given Year", x = "Year", y = "Number of Songs") + theme_classic()
```

The line graph above depicts the diversity trend in the music industry as indicated by the number of unique songs on the Billboard Top 100 chart every year. The number of unique songs increased from 1959 to 1967, but it experienced a steep decline from 1968 to 2001. It reached its lowest point in 2001, and rose rapidly from 2004 onwards. 



Part C: Let’s define a “ten-week hit” as a single song that appeared on the Billboard Top 100 for at least
ten weeks. There are 19 artists in U.S. musical history since 1958 who have had at least 30 songs that were
“ten-week hits.” Make a bar plot for these 19 artists, showing how many ten-week hits each one had in their
musical career. Give the plot an informative caption in which you explain what is shown.

```{r echo=FALSE}
ten_week = top_song %>%
  filter(count_total >= 10) %>%
  group_by(performer) %>%
  summarize(num = n()) %>%
  filter(num >= 30)

ggplot(ten_week) + geom_col(aes(x = performer, y = num), fill = 'pink') + labs(title = "Artists With 30+ Songs On Billboard Top 100 for At Least 10 Weeks", x = "Artist Name", y = "Number of Songs") + coord_flip() + theme_classic()
```

The bar plot above shows 19 artists with over 30 songs that stayed on the Billboard Top 100 chart for over 10 weeks, along with the exact number of songs that were on the chart over 10 weeks. Among the singers, Brad Paisley, Daryl Hall John Oates, George Strait, Jason Aldean, and Neil Diamond had the smallest number of popular song with 30 songs on the list. On the other hand, Elton John had the most popular songs among the 19 artists, sitting at an astonishing 52 songs that remained on the Billboard Top 100 chart for over 10 weeks.
