---
title: "HW 3"
author: "Kate Kong jk49633"
date: "2024-02-04"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

creatinine <- read.csv('creatinine.csv')
covid <- read.csv('covid.csv')
marketmodel <- read.csv('marketmodel.csv')
milk <- read.csv('milk.csv')

library(ggplot2)
library(dplyr)
suppressPackageStartupMessages(library(tidyverse))
```

# Link to the GitHub
[GitHub](https://github.com/katekong27/SDS_315.git)


# **Question 1**

You can also embed plots, for example:

```{r echo=FALSE, warning=FALSE, message=FALSE}
plot <- ggplot(creatinine)

plot + geom_point(aes(x=age, y=creatclear)) + geom_smooth(aes(x=age, y=creatclear), method='lm')

model_hr = lm(creatclear ~ age, data=creatinine)
regdata <- coef(model_hr)

regline <- function(x) {
  output <- x * regdata[2]
  output2 = output + regdata[1]
  return(output2)
}
```

A) We should expect a creatinine clearance rate of `r round(as.numeric(regline(55)), 3)` for a 55 year old.

B) The creatinine clearance rate decreases by `r round(as.numeric(abs(regdata[2])), 3)` ml/minute per year because the slope of the linear regression line is `r round(as.numeric(regdata[2]), 3)`.

C) The expected creatinine clearance rate for a 40 year old is `r round(as.numeric(regline(40)), 3)`ml/ minute. The expected creatinine clearance rate for a 60 year old is `r round(as.numeric(regline(60)), 3)` m;/minute. Between 135 - `r round(as.numeric(regline(40)), 3)` = `r 135 - round(as.numeric(regline(40)), 3)` and 112 - `r round(as.numeric(regline(60)), 3)` = `r 112 - round(as.numeric(regline(40)), 3)', the former has the bigger difference. Therefore, a 40 year old with a rate of 135 ml/minute is healthier than a 60 year old with a rate of 112 m;/minute. 

# **Question 2**
The beta of a company is a measure of systematic risk depending on the market portfolio. It is calculated in terms of percentages, so if a company has a beta of 0.05, its value increases by 0.05% every time the market increases by 1%. If the value of the beta for a specific company is a negative value, it means its value increases by the percentage point every time the market value DECREASES by 1%. 

```{r echo=FALSE, warning=FALSE, message=FALSE}

```



# **Question 3**

```{r echo=FALSE, warning=FALSE, message=FALSE}
covid2 = covid %>%
  filter(country == "Italy")
lm_italy = lm(log(deaths) ~ days_since_first_death, data=covid2)
coef(lm_italy)

covid3 = covid %>%
  filter(country == "Spain")
lm_spain = lm(log(deaths) ~ days_since_first_death, data=covid3)
coef(lm_spain)

ggplot(covid) + geom_line(aes(x = days_since_first_death, y = log(deaths), color = country)) + scale_color_brewer(type='qual') + scale_y_log10() + labs(title = "Line Graph of COVID Deaths in Italy and Spain Since the Day of the First Death", x = "Days since first death", y = "Deaths")

```

1. The estimated growth rate for Italy is 18.322%. 
2. The estimated growth rate for Spain is 27.624%. 
3. Graph is shown above

# **Question 4**

```{r echo=FALSE}
lm_milk = lm(log(sales) ~ price, data=milk)
coef(lm_milk)
```

I believe the price elasticity is -0.54, meaning for every $1 increase in milk pice, the sales decrease by 0.54%. 
