---
title: "HW 04"
author: "Kate Kong jk49633"
date: "2024-02-19"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

gasprices <- read.csv('gasprices.csv')
sclass <- read.csv('sclass.csv')
nbc_pilotsurvey <- read.csv('nbc_pilotsurvey.csv')
ebay <- read.csv('ebay.csv')

library(ggplot2)
library(dplyr)
suppressPackageStartupMessages(library(tidyverse))
library(mosaic)
```

# Link to the GitHub
[GitHub](https://github.com/katekong27/SDS_315.git)

# **Question 1**

## Part A
The first theory states, "Gas stations charge more if they lack direct competition in sight." 

```{r echo=FALSE}
n = 10

comp = gasprices %>%
  filter(Competitors == "Y")
comp_mean <- mean(~Price, data=comp)
comp_sample <- do(100)*mean(~Price, data=sample(comp, size=n))
comp_sd <- sd(~Price, data=comp)

nocomp = gasprices %>% 
  filter(Competitors == "N")
nocomp_mean <- mean(~Price, data = nocomp)
nocomp_sample <- do(100)*mean(~Price, data=sample(nocomp, size=n))
nocomp_sd <- sd(~Price, data=nocomp)

ggplot(comp_sample) + geom_histogram(aes(x = mean), binwidth = 0.005) + labs(title = "Distribution of Sampled Gas Prices at Gas Stations with Competition", x = "Gas Price", y = "Frequency") + geom_vline(xintercept = comp_mean, color='blue')

ggplot(nocomp_sample) + geom_histogram(aes(x = mean), binwidth = 0.005) + labs(title = "Distribution of Sampled Gas Prices at Gas Stations without Competition", x = "Gas Price", y = "Frequency") + geom_vline(xintercept = nocomp_mean, color='blue')
```

According to the data and the graph, the mean gas price for gas stations with competitors nearby is `r round(comp_mean, 2)` dollars, with a standard error of `r round(comp_sd, 2)` dollars. This gives us a confidence interval of `r (round(comp_mean, 2) - round(comp_sd, 2))` dollars to `r (round(comp_mean, 2) + round(comp_sd, 2))` dollars for the mean of gas prices for gas stations with competitors. On the other hand, the mean gas price for gas stations without competitors is `r round(nocomp_mean, 2)` dollars, with a standard error of `r round(nocomp_sd, 2)` dollars. This gives us a confidence interval of `r (round(nocomp_mean, 2) - round(nocomp_sd, 2))` dollars to `r (round(nocomp_mean, 2) + round(nocomp_sd, 2))` dollars for the mean of gas prices for gas stations without competitors. Gas stations without competitors have a higher mean gas price by `r (round(nocomp_mean, 2) - round(comp_mean, 2))` dollars. Not only that, but their confidence intervals are also higher than those of gas stations without competitors by `r ((round(nocomp_mean, 2) - round(nocomp_sd, 2)) - (round(comp_mean, 2) - round(comp_sd, 2)))` dollars to `r ((round(nocomp_mean, 2) + round(nocomp_sd, 2)) - (round(comp_mean, 2) + round(comp_sd, 2)))` dollars. Based on these figures, it can be concluded that gas stations charge their customers higher prices if there is a lack of competition surrounding them. Therefore, the theory is supported by the data. 


## Part B
Your discussion of each theory should include three mini-sections:
- Claim: a statement of the theory itself.
- Evidence: the evidence for or against the theory, in the form of any relevant numerical and/or visual
summaries If the theory looks correct, provide an estimate of the effect size: that is, how large is the difference
(e.g. for highway vs. non-highway gas stations) and/or association (e.g. between income and price)? If the
theory is unsupported by the data, explain why.
- Conclusion: your conclusion about whether the theory is supported or unsupported by the data.

B) The richer the area, the higher the gas prices.

```{r echo=FALSE}
rich = gasprices
ggplot(rich) + geom_point(aes(x = Income, y = Price)) + labs(title = "Relationship Between Average Income of the Area and Its Gas Price", x = "Income", y = "Gas Price")

```

C) Gas stations at stoplights charge more.

```{r echo=FALSE}


```

D) Gas stations with direct highway access charge more.

```{r echo=FALSE}


```

E) Shell charges more than all other non-Shell brands.

```{r echo=FALSE}
shell = gasprices %>%
  mutate(isShell = (Name == "Shell"))

notshell = shell %>%
  filter(isShell == FALSE)

shell %>%
  filter(isShell == TRUE)

nocomp_mean <- mean(~Price, data = nocomp)
nocomp_sample <- do(100)*mean(~Price, data=sample(nocomp, size=n))
nocomp_sd <- sd(~Price, data=nocomp)

ggplot(shell) + geom_histogram(aes(x = Price), binwidth = 0.01) + labs(title = "Distribution of Gas Prices for Shell / Non-Shell Gas Stations", x = "Gas Price", y = "Frequency") + facet_wrap(~isShell)
```



# **Question 2**

## Part A

```{r echo=FALSE}
sclass2 = sclass %>%
  filter(year == 2011 & trim == "63 AMG")

boot_63 = do(1000)*mean(~mileage, data=mosaic::resample(sclass2))
confidence_63 = confint(boot_63, level = 0.95)
confidence_63
```

Given that the confidence level is 95%, the bootstrap confidence interval for the average mileage of 2011 S-Class 63 AMGs in the used-car market ranges from `r round(as.numeric(confidence_63[1, 2]), 3)` to `r round(as.numeric(confidence_63[1, 3]), 3)` mph.

## Part B

```{r echo=FALSE}
sclass3 = sclass %>%
  filter(year == 2014 & trim == "550") %>%
  mutate(isBlack = (color == "Black"))

boot_550 = do(10000)*prop(~isBlack, data=mosaic::resample(sclass3))
confidence_550 = confint(boot_550, level = 0.95)
confidence_550
```

With a confidence level of 95%, the bootstrap confidence interval for the proportion of black vehicles among the used 2014 S-Class 550s in the market ranges from `r round(as.numeric(confidence_550[1, 2]), 3)` to `r round(as.numeric(confidence_550[1, 3]), 3)` mph.

# **Question 3**
1) Question: What question are you trying to answer?
2) Approach: What approach/statistical tool did you use to answer the question?
3) Results: What evidence/results did your approach provide to answer the question? (E.g. any numbers,
tables, figures as appropriate.)
4) Conclusion: What is your conclusion about your question? Provide a written interpretation of your
results, understandable to stakeholders who might plausibly take an interest in this data set.


Part A. Consider the shows “Living with Ed” and “My Name is Earl.” Who makes people happier: Ed or
Earl? Construct a filtered data set containing only viewer responses where Show == "Living with Ed" or
Show == "My Name is Earl". Then construct a 95% confidence interval for the difference in mean viewer
response to the Q1_Happy question for these two shows. Is there evidence that one show consistently produces
a higher mean Q1_Happy response among viewers?

```{r echo=FALSE}
happy_ed = nbc_pilotsurvey %>%
  filter(Show == "Living with Ed")
mean_ed = mean(~Q1_Happy, data = happy_ed)
boot_ed = do(1000)*mean(~Q1_Happy, data=mosaic::resample(happy_ed))
confidence_ed = confint(boot_ed, level = 0.95)

happy_earl = nbc_pilotsurvey %>%
  filter(Show == "My Name is Earl")
mean_earl = mean(~Q1_Happy, data = happy_earl)
boot_earl = do(1000)*mean(~Q1_Happy, data=mosaic::resample(happy_earl))
confidence_earl = confint(boot_earl, level = 0.95)
as.numeric(confidence_earl[1, 6])
```

The question that is being investigated in this section is who makes people happier between Ed and Earl. To answer the question, bootstrapping was used. 

Consider the shows “The Biggest Loser” and “The Apprentice: Los Angeles.” Which reality/contest
show made people feel more annoyed? Construct a filtered data set containing only viewer responses
where Show == "The Biggest Loser" or Show == "The Apprentice: Los Angeles". Then construct a
95% confidence interval for the difference in mean viewer response to the Q1_Annoyed question for these two
shows. Is there evidence that one show consistently produces a higher mean Q1_Annoyed response among
viewers?

```{r echo=FALSE}


```




# **Question 4**

Your task is to compute the difference in revenue ratio between the treatment and control DMAs and provide a 95% confidence interval for the difference. Use these results to assess the evidence for whether the revenue ratio is the same in the treatment and control groups, or whether instead the data favors the idea that paid search advertising on Google creates extra revenue for EBay. Make sure you use at least 10,000 Monte Carlo simulations in any bootstrap simulations.

Your write-up for this problem should include four sections:
1) Question: What question are you trying to answer?
2) Approach: What approach/statistical tool did you use to answer the question?
3) Results: What evidence/results did your approach provide to answer the question? (E.g. any numbers,
tables, figures as appropriate.)
4) Conclusion: What is your conclusion about your question? Provide a written interpretation of your
results, understandable to stakeholders who might plausibly take an interest in this data set.

if rev_ratio < 1, rev_after is lower than rev_below

```{r echo=FALSE}
mean_rev_ratio = mean(rev_ratio ~ adwords_pause, data=ebay)
mean_diff_ratio = diffmean(rev_ratio ~ adwords_pause, data=ebay)

boot_ebay = do(10000)*diffmean(rev_ratio ~ adwords_pause, data=mosaic::resample(ebay))
ggplot(boot_ebay) + geom_histogram(aes(x=diffmean), binwidth = 0.005)
confint(boot_ebay, level = 0.95)
```

The goal for this analysis is to figure out whether paid search advertising bring in extra revenue to Ebay. To analyze the data, the bootstrapping method was used. First, the difference in mean revenue ratio for treatment and control groups were `r round(mean_diff_ratio, 3)`, where the mean ratio for the treatment group (paid Google advertisement stopped) was `r round(as.numeric(mean_rev_ratio[2]), 3)` and the mean ratio for the control group (paid Google advertisement continued) was `r round(as.numeric(mean_rev_ratio[1]), 3)`. Then, we ran 10,000 Monte Carlo simulations using samples of 


